---
output: html_document
editor_options: 
  chunk_output_type: console
---


```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center', fig.width = 8, fig.height = 8)
knitr::opts_knit$set(root.dir = here::here())
```
```{r}
library(tidyverse)
source("R/themes.R")
```

# Section I: Low-Hanging Fruit 

In this section .... 

## Differentiating Mass Action and Degree Distribution
Here, we can compare our simualted degree distribution results versus the mass action model results to approximate the point of divergence using the KL divergence formula. We can then contrast this with Newman's equation predictions. This is a precursor to *Section II*, which explores the _Gdoc Question "How does the variance in the final size distribution change as we vary properties of the network?"_


Trans on Y deg dist on X color is MA vs Newman
run MA one hundred for each transm 
\textcolor{red}{To plot from "corrected" simulations}
```{r}
```



## Mass Action vs Dynamicity 
For modeling dynamicity of contacts, we used the neighbor exchange method presented by [Volz and Meyer 2007](https://pubmed.ncbi.nlm.nih.gov/17878137/). In their subsequent manuscript, [Volz and Meyer 2009](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC2659580/) show that once can solve the NE model in a closed form approximation and predict final sizes. They state that the NE converges to a mass action model as the mixing rate has $\lim_{\rho \rightarrow \infty}$ (paragraph above discussion). To answer the _Gdoc Question "Using the Neighbor Exchange (NE) model of Volz and Meyers (), we could explore how the intrinsic variability in final sizes changes as we go from a full static network (rho=0) to a random mixing model (rho=1)"_: We can recapitulate this result by picking one of our degree distributions from above that approximated a mass action model well (arbitrarily DD = 0.95) and continually increase the NE mixing rate, \rho, to see a decrease in the KL divergence.  

\textcolor{red}{To run these simulations w/ specific DD and rhos}
```{r}
```
