---
output: html_document
editor_options: 
  chunk_output_type: console
---

# Stochastic Noise from Network Attributes
In this section, we explore the network attributes that generate the greatest variation in the distribution of final sizes _Gdoc Question: "How does the variance in the final size distribution change as we vary properties of the network?")_. To do so, we used a closed population, stochastic continuous-time agent-based SIR model implemented with the Gillespie algorithm and the [fomes](https://github.com/TriCEM/fomes) package with inputs for: $\beta$, $\gamma$, contact-network, population-size, initial number of infected. 

For all simulations, population size was fixed at N = 1000. Initial seed infections were set at 1 (infect seed = 1).  We used an adaptive simulated annealing strategy to find the "phase transitions" in the epidemic, or the parameter space that maximized the variance in the final size distribution given a contact network. Initial values of $\beta$, or the probability of transmission/transmission coefficient given the contact via network were: `betaI <-seq(0.1, 1, by = 0.2)`. Similarly, initial values of $\gamma$, or the rate of recover ($\frac{1}{duration})$, were: `durationI <- seq(3, 15, by = 3)`.

For contact network structure, we 10 base networks with the same degree sequence for each node (**degree = 50**). These base networks were then manipulated to have varying network characteristics: degree distribution (homogenous degree variance and heterogenous degree variance), modularity, clustering, and dynamicity. 




```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center', fig.width = 8, fig.height = 8)
knitr::opts_knit$set(root.dir = here::here())
```
```{r}
library(tidyverse)
library(cowplot)
source("R/themes.R")
```


```{r}

#++++++++++++++++++++++++++++++++++++++++++ 
### Munging        ####
#++++++++++++++++++++++++++++++++++++++++++
#......................
# unpack data
#......................
simruns <- list.files("data/derived_data/", pattern = ".RDS", full.names = TRUE)
simruns <- lapply(simruns, function(x){
  ret <- readRDS(x)
  ret <- ret %>% 
    dplyr::mutate(outname = basename(x))
  return(ret)
})
simruns <- dplyr::bind_rows(simruns)

#......................
# TEMPORARY
# TODO fix this munging once you haven't collated a billino strings
#......................
simruns <- simruns %>% 
  dplyr::mutate(
    net = stringr::str_replace(net, "b0", "base_0"),
    mod = stringr::str_split_fixed(basename(net), "_", n = 4)[,1],
    manip = stringr::str_split_fixed(basename(net), "_", n = 4)[,2],
    val = stringr::str_split_fixed(basename(net), "_", n = 4)[,3],
    bnet = stringr::str_split_fixed(basename(net), "_", n = 4)[,4],
    bnet = stringr::str_replace(bnet, ".RDS", ""),
    extraval = stringr::str_split_fixed(val, "-", n = 2)[,2], # deg dist
    val = ifelse(stringr::str_detect(val, "-"), 
                 stringr::str_split_fixed(val, "-", n = 2)[,1],
                 val),
    val = as.numeric(val),
    extraval = as.numeric(extraval))

#......................
# catch NE 
#......................
simruns <- simruns %>% 
  dplyr::mutate(
    mod = ifelse(
                stringr::str_detect(outname,"NEdynamicityexchrate"), 
                "NE", 
                mod
              ),
    val = ifelse(
                stringr::str_detect(outname,"NEdynamicityexchrate"), 
                as.numeric(stringr::str_extract(outname, "(?<=rate).*(?=-)")),
                val
              )
    )


#......................
# add in Transmission Probability
# T = 1 - e^(- \beta * \frac{1}{\gamma})
# Newman 2002
#......................
simruns <- simruns %>% 
  dplyr::mutate(TransProb = 1 - exp(- beta * durI))

#......................
# Factorize Bnet
#......................
simruns <- simruns %>% 
  dplyr::mutate(BaseNet = factor(bnet, levels = 1:10, labels = paste0("Net", 1:10)))



#......................
# split up data 
# have to do this manually given different graphs later
#......................

# base
basesims <- simruns %>% 
  dplyr::filter(mod == "base") %>% 
  dplyr::select(-c("manip", "val", "extraval")) %>% 
  tidyr::unnest(cols = SAout)

# dd
degreedistsims <- simruns %>% 
  dplyr::filter(mod == "degreedist") %>% 
  dplyr::rename(mean = val,
                variance = extraval) %>% 
  tidyr::unnest(cols = SAout)

# cluster
clustersims <- simruns %>% 
  dplyr::filter(mod == "cluster") %>% 
  dplyr::rename(clustercoef = val) %>% 
  tidyr::unnest(cols = SAout)

# modularity 
modularitysims <- simruns %>% 
  dplyr::filter(mod == "modularity") %>% 
  dplyr::rename(dropedges = val) %>% 
  tidyr::unnest(cols = SAout)

# unity 
unitysims <- simruns %>% 
  dplyr::filter(mod == "unity") %>% 
  dplyr::rename(addedges = val) %>% 
  tidyr::unnest(cols = SAout)

# dynamicity 
NEsims <- simruns %>% 
  dplyr::filter(mod == "NE") %>% 
  dplyr::rename(exchangerate = val) %>% 
  tidyr::unnest(cols = SAout)


```

## Analyzing Simulation Variance across Networks
_NB_ for plotting tractability, we have subsetted to 10-25% of repetitions of final sizes collected from each adaptive simulated annealing simulations. 

### Base Plots
These are the 10 base plots without any network manipulations. Remember, the initial degree distribution was set to 50 for each node.
```{r}

#++++++++++++++++++++++++++++++++++++++++++ 
### Base Plot        ####
#++++++++++++++++++++++++++++++++++++++++++
lbls <- mapply(function(x,y){mean(c(x,y))}, x = seq(0, 1, length.out = 11), y = dplyr::lead(seq(0, 1, length.out = 11)))[1:10]
basesims$TransProbFct <- cut(basesims$TransProb, breaks = seq(0, 1, length.out = 11), include.lowest = TRUE,
                             labels = lbls)

# expand out 
basesims <- basesims %>% 
  tidyr::unnest(cols = finalsize) %>%   
  dplyr::mutate(finalsize = finalsize/1e3) 
# downsize
keep <- sample(x = c(T,F), size = nrow(basesims), replace = T, prob = c(0.25, 0.75))
basesimssm <- basesims %>% 
  dplyr::filter(keep)


# plot
basenetPlotObj <- basesimssm %>% 
  ggplot() + 
  geom_boxplot(aes(x = TransProbFct, y = finalsize,
                   fill = factor(BaseNet))) +
  scale_fill_viridis_d("Base Networks") + 
  ylab("Final Size Distribution") + 
  xlab("Probability of Transmission") + 
  plot_theme

# call to RMD 
basenetPlotObj

# save out
jpeg("figures/base_network_final_size_distribution_from_simulations.jpg",
     width = 11, height = 8, units = "in", res = 500)
basenetPlotObj
graphics.off()



```

### Degree Distribution
In addition to the probability of degree connectedness varying, for each node the variance of connections was also varied node using a stick-breaking approach. 
```{r}

#++++++++++++++++++++++++++++++++++++++++++ 
### Degree Dist Plot        ####
#++++++++++++++++++++++++++++++++++++++++++
# expand out 
degreedistsims <-  degreedistsims %>% 
  tidyr::unnest(cols = finalsize) %>%   
  dplyr::mutate(finalsize = finalsize/1e3) 

# downsize
keep <- sample(x = c(T,F), size = nrow(degreedistsims), replace = T, prob = c(0.10, 0.9))
degreedistsimssm <- degreedistsims %>% 
  dplyr::filter(keep)

# plot 
degreedistnetPlotObj <- degreedistsimssm %>% 
  ggplot() + 
  geom_jitter(aes(x = TransProb, y = finalsize, 
                  color = factor(mean), 
                  size = variance,
                  shape = BaseNet),
              alpha = 0.1) +
  scale_colour_viridis_d("Degree Dist. Prob.") +
  scale_shape_manual("Base Net.", 
                     values = c(1, 2, 3, 4, 6, 15, 18, 19, 24, 25)) +
  scale_size_continuous("Degree Dist. Var.") +
  ylab("Final Size Distribution") + 
  xlab("Probability of Transmission") + 
  plot_theme +
  guides(color = guide_legend(override.aes = list(alpha = 1)))


# call to RMD 
degreedistnetPlotObj

# save out
jpeg("figures/degreedist_network_final_size_distribution_from_simulations.jpg",
     width = 11, height = 8, units = "in", res = 200)
degreedistnetPlotObj
graphics.off()

```

### Clustering 
Varied the clustering coefficient (number of triangles) in the network. 
```{r}

#++++++++++++++++++++++++++++++++++++++++++ 
### Cluster Plot        ####
#++++++++++++++++++++++++++++++++++++++++++
# expand out 
clustersims <-  clustersims %>% 
  tidyr::unnest(cols = finalsize) %>%   
  dplyr::mutate(finalsize = finalsize/1e3) 

# downsize
keep <- sample(x = c(T,F), size = nrow(clustersims), replace = T, prob = c(0.10, 0.9))
clustersimssm <- clustersims %>% 
  dplyr::filter(keep)

# plot 
clusternetPlotObj <- clustersimssm %>% 
  ggplot() + 
  geom_jitter(aes(x = TransProb, y = finalsize, 
                  color = factor(clustercoef), 
                  shape = BaseNet),
              alpha = 0.1) +
  scale_colour_viridis_d("Cluster Coeff.") +
  scale_shape_manual("Base Net.", 
                     values = c(1, 2, 3, 4, 6, 15, 18, 19, 24, 25)) +
  xlab("Probability of Transmission") + 
  ylab("Final Size Distribution") + 
  plot_theme  +
  guides(color = guide_legend(override.aes = list(alpha = 1)))


# call to RMD 
clusternetPlotObj

# save out
jpeg("figures/clustering_network_final_size_distribution_from_simulations.jpg",
     width = 11, height = 8, units = "in", res = 500)
clusternetPlotObj
graphics.off()

```

### Modularity/Unity
#### Removing Edges
From each base network, we removed the most connected `c(5, 10, 15, 25, 50, 100, 250, 500, 750, 1000)` edges. High edge betweenness identified with `igraph::betweeness` and randomly removed X set of those edges.

```{r}
#++++++++++++++++++++++++++++++++++++++++++ 
### Remove Edge Plot        ####
#++++++++++++++++++++++++++++++++++++++++++
# expand out 
modularitysims <-  modularitysims %>% 
  tidyr::unnest(cols = finalsize) %>%   
  dplyr::mutate(finalsize = finalsize/1e3) 

# downsize
keep <- sample(x = c(T,F), size = nrow(modularitysims), replace = T, prob = c(0.10, 0.9))
modularitysimssm <- modularitysims %>% 
  dplyr::filter(keep)

# plot 
modularitynetPlotObj <- modularitysimssm %>% 
  ggplot() + 
  geom_jitter(aes(x = TransProb, y = finalsize, 
                  color = factor(dropedges), 
                  shape = BaseNet),
              alpha = 0.1) +
  scale_colour_viridis_d("Edges Dropped") +
  scale_shape_manual("Base Net.", 
                     values = c(1, 2, 3, 4, 6, 15, 18, 19, 24, 25)) +
  xlab("Probability of Transmission") + 
  ylab("Final Size Distribution") + 
  plot_theme  +
  guides(color = guide_legend(override.aes = list(alpha = 1)))


# call to RMD 
modularitynetPlotObj

# save out
jpeg("figures/modularity_network_final_size_distribution_from_simulations.jpg",
     width = 11, height = 8, units = "in", res = 500)
modularitynetPlotObj
graphics.off()

```


#### Adding Edges 
As above, but the oppoite of modularity when starting w/ a base. From each base network, we add the most connected c(5, 10, 15, 25, 50, 100, 250, 500, 750, 1000) (10 parameters) edges that could potentially exist in the completely saturated base graph.

```{r}

#++++++++++++++++++++++++++++++++++++++++++ 
### Add Edge Plot        ####
#++++++++++++++++++++++++++++++++++++++++++
# expand out 
unitysims <-  unitysims %>% 
  tidyr::unnest(cols = finalsize) %>%   
  dplyr::mutate(finalsize = finalsize/1e3) 

# downsize
keep <- sample(x = c(T,F), size = nrow(unitysims), replace = T, prob = c(0.10, 0.9))
unitysimssm <- unitysims %>% 
  dplyr::filter(keep)

# plot 
unitynetPlotObj <- unitysimssm %>% 
  ggplot() + 
  geom_jitter(aes(x = TransProb, y = finalsize, 
                  color = factor(addedges), 
                  shape = BaseNet),
              alpha = 0.1) +
  scale_colour_viridis_d("Edges Added") +
  scale_shape_manual("Base Net.", 
                     values = c(1, 2, 3, 4, 6, 15, 18, 19, 24, 25)) +
  xlab("Probability of Transmission") + 
  ylab("Final Size Distribution") + 
  plot_theme  +
  guides(color = guide_legend(override.aes = list(alpha = 1)))


# call to RMD 
unitynetPlotObj

# save out
jpeg("figures/unity_network_final_size_distribution_from_simulations.jpg",
     width = 11, height = 8, units = "in", res = 500)
unitynetPlotObj
graphics.off()

```


### Dynamicity 
We used the [Volz & Meyer 2007](https://pubmed.ncbi.nlm.nih.gov/17878137/) neighbor exchange model to explore the effects of a dynamic network on prediction. The neighbor exchange, or swap, rate parameter was varied on a logarithmic-10 scale from 1e-9 to 1 (10 parameters): `sapply(seq(10, 1), function(x){10^(-x)}))`. _N.B._ the transmission probability by [Newman 2002](https://www.math.uh.edu/~zpkilpat/teaching/math4309/project/pre02_newman.pdf) is only valid for static networks and is therefore misspecified here. 

```{r}

#++++++++++++++++++++++++++++++++++++++++++ 
### Add Edge Plot        ####
#++++++++++++++++++++++++++++++++++++++++++
# expand out 
NEsims <-  NEsims %>% 
  tidyr::unnest(cols = finalsize) %>%   
  dplyr::mutate(finalsize = finalsize/1e3) 
  
# downsize
keep <- sample(x = c(T,F), size = nrow(NEsims), replace = T, prob = c(0.10, 0.9))
NEsimssm <- NEsims %>% 
  dplyr::filter(keep)

# plot 
NEnetPlotObj <- NEsimssm %>% 
  ggplot() + 
  geom_jitter(aes(x = TransProb, y = finalsize, 
                 color = factor(exchangerate), 
                 shape = BaseNet),
              alpha = 0.1) +
  scale_colour_viridis_d("Neigh. Exch. Rate") +
  scale_shape_manual("Base Net.", 
                     values = c(1, 2, 3, 4, 6, 15, 18, 19, 24, 25)) +
  xlab("Probability of Transmission") + 
  ylab("Final Size Distribution") + 
  plot_theme  +
  guides(color = guide_legend(override.aes = list(alpha = 1)))


# call to RMD 
NEnetPlotObj

# save out
jpeg("figures/NEdyanamicity_network_final_size_distribution_from_simulations.jpg",
     width = 11, height = 8, units = "in", res = 500)
NEnetPlotObj
graphics.off()

```



### Collated
```{r}
# combin the plots 
combplot <- cowplot::plot_grid(basenetPlotObj, degreedistnetPlotObj, clusternetPlotObj, modularitynetPlotObj, unitynetPlotObj, NEnetPlotObj, 
                   nrow = 3, ncol = 2)


top <- cowplot::plot_grid(basenetPlotObj, degreedistnetPlotObj, ncol = 2)
mid <- cowplot::plot_grid(modularitynetPlotObj, unitynetPlotObj, ncol = 2)
bottom <- cowplot::plot_grid(clusternetPlotObj, NEnetPlotObj, ncol = 2)
combplot <- cowplot::plot_grid(top, mid, bottom, nrow = 3, ncol = 1)




jpeg("figures/combined_network_final_size_distribution_from_simulations.jpg",
     width = 24, height = 27, units = "in", res = 500)
combplot
graphics.off()

```
