---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r, include=FALSE}
knitr::opts_chunk$set(echo = T, warning = F, message = F, eval = T, results = 'hide',
                      fig.align = 'center', fig.width = 8, fig.height = 8)
knitr::opts_knit$set(root.dir = here::here())
```
```{r}
library(fomes)
library(tidyverse)
library(DT)
source("R/KLdiverg.R")
source("R/themes.R")
```

```{r}
#............................................................
# read in and extract relevant information from simulations
#...........................................................
fns <- list.files("simulations/01_generated_simulation_runs/", recursive = T, pattern = ".RDS", full.names = T)
fns <- fns[stringr::str_detect(fns, "log", negate = T)] # drops logs
# need bias
biasfns <- fns[stringr::str_detect(fns, "BIAS", negate = F)]
# need OG as well
ogfns <- fns[stringr::str_detect(fns, "BIAS", negate = T)]


```

# Divergence with Observation Bias Introduced
In this section, we have introduced "observation bias" into our networks at the following levels: 1%, 5%, 10%. Observation bias was created by randomly selecting the x% edges (and potential edges) previously described and randomly erasing or adding them. This section aims to answer the question: _"How much observation bias can be introduced into a network before the variance in the final size distribution noticeably changes?")_. 

```{r}
#............................................................
# og fxn
#...........................................................
#............................................................
# extract relevant information
#...........................................................
# each OG RDS is a 100 indiviudal reps/realizations of a fomes model given a beta and durI w/r/t a netpath and val of that netpath 
OGextractfs <- function(pth) {
  ret <- readRDS(pth)
  ret %>% 
    dplyr::mutate(basenet = stringr::str_extract(basename(unique(ret$netpath)), "(?<=_)[0-9]+(?=\\.RDS$)")) %>% 
    dplyr::mutate(fs = purrr::map_dbl(fomesout, "FinalEpidemicSize")) %>%  
    dplyr::select(-c("seed", "fomesout")) %>% 
    dplyr::group_by(mod, beta, durI, val, basenet) %>% 
    tidyr::nest(finalsizes = fs)
}
#......................
# make results tbl
#......................
ogsimrets <- lapply(ogfns, OGextractfs) %>% 
  dplyr::bind_rows()

#............................................................
# bias fxm
#...........................................................
Biasextractfs <- function(pth) {
  
  ret <- readRDS(pth)
  ret %>% 
    dplyr::mutate(basenet = stringr::str_extract(basename(unique(ret$netpath)), "(?<=_)[0-9]+(?=\\.RDS$)")) %>% 
    dplyr::mutate(biasfs = purrr::map_dbl(biasfomesout, "FinalEpidemicSize")) %>%  
    dplyr::select(-c("seed", "biasfomesout")) %>% 
    dplyr::group_by(mod, beta, durI, val, basenet, bias) %>% 
    tidyr::nest(biasfinalsizes = biasfs)
}

#......................
# make results tbl
#......................
biassimrets <- lapply(biasfns, Biasextractfs) %>% 
  dplyr::bind_rows()

```

```{r}
#............................................................
# make generalizable plot function
#...........................................................
plotBiasSimRet <- function(df, modname) {
  #......................
  # capture our subset conditions   
  #......................
  enqmodname <- rlang::enquo(modname)
  #......................
  # subset to plot df  
  #......................
  plotdf <- df %>% 
    dplyr::filter(mod == !!enqmodname) 
    #dplyr::filter(beta == !!enqbeta) %>% 
    #dplyr::filter(durI == !!enqdurI)
  #......................
  # plotting items that are project specific 
  #......................
  # betas and durI 
  transmvls <- tidyr::expand_grid(betaI = c(0.005, 0.01, 0.05, 0.075, 0.1), durationI = seq(3, 15, by = 3)) %>% 
    dplyr::mutate(bd = purrr::map2_dbl(betaI, durationI, function(x,y){ 1 - (1-x)^y }),
                  bd = round(bd,4)) %>% 
    dplyr::arrange(bd) %>% 
    dplyr::mutate(bd = as.character(bd)) %>% 
    dplyr::pull(bd)
  
  # lvls
  if (modname == "degreedist") {
    mylvls <- tidyr::expand_grid(x = c(0.05, 0.1, 0.15, 0.2, 0.25), y = c(0, 1, 5, 10, 25)) %>%
      dplyr::mutate(val = purrr::map2_chr(x, y, function(x, y){paste(x, y, sep = "-")})) %>% 
      dplyr::pull(val)
  } else {
    mylvls <- as.character( sort(unique(as.numeric(plotdf$val))) )
  }
  
  # plot
  plotObj <- plotdf %>% 
    dplyr::mutate(valfct = factor(val, levels = mylvls, ordered = T),
                  transmission = 1 - (1-beta)^durI,
                  transmission = round(transmission, 4),
                  transmission_fct = factor(transmission, levels = transmvls, ordered = T)) %>% 
    ggplot() + 
    geom_boxplot(aes(x = valfct, y = KLdiverg, color = transmission_fct),
                 outlier.shape = 8,
                 position = position_dodge(width = 0.6),
                 alpha = 0.5) +
    scale_color_viridis_d("Transmission") +
    plot_theme + 
    theme(axis.text.x = element_text(hjust = 0.5, vjust = 0.6, size = 11, angle = 45)) +
    xlab("Net Value Manipulation") + ylab("KL Divergence between Full and Biased Sims") + 
    labs(caption = "Transmission is a binomial approximation w/r/t prob. of infxn and duration of illness.")
  plot(plotObj)
  # plotly
  #plotly::ggplotly(plotObj)
}

#............................................................
# Combine two Results and calculate KL
#...........................................................
combrets <- dplyr::left_join(ogsimrets, biassimrets, 
                             by = c("mod", "beta", "durI", "val", "basenet"))

# wrapper fxn
KLdivpqcont_wrapper <- function(finalsizes, biasfinalsizes, N) {
  out <- KLdivpqcont(p_empdat = finalsizes$fs, q_empdat = biasfinalsizes$biasfs, N = N)
  return( out$integral )
}

combrets <- combrets %>% 
  dplyr::mutate(KLdiverg = purrr::map2_dbl(finalsizes, biasfinalsizes, KLdivpqcont_wrapper, 
                                           N = 1000))
```

### Degree Distribution
```{r}
plotBiasSimRet(df = combrets, modname = "degreedist")
```

### Modularity
```{r}
plotBiasSimRet(df = combrets, modname = "modularity")
```

### Unity
```{r}
plotBiasSimRet(df = combrets, modname = "Unity")
```

### Clustering
```{r}
plotBiasSimRet(df = combrets, modname = "cluster")
```

### Dynamicity
```{r}
plotBiasSimRet(df = combrets, modname = "NEdynamicity")
```
